\chapter*{Acknowledgements}
First and foremost, I would like to express my deepest thanks to my principal supervisor Professor Hiromichi Fukui for his patient guidance and constant support throughout my three years of studies. His broad vision has significantly influenced my journey during my Ph.D. His mentorship goes beyond academic matters, assisting me in navigating life in Japan. I am sincerely thankful for his encouragement and constructive feedback on my research, paper writing, and the draft of this thesis. I feel incredibly fortunate to have been his student and to have had the opportunity to work with him. \par

I would like to express my deep appreciation to Mr. Kyoshi Takejima for his kind support and guidance. He has taught me the basics and fundamentals of local forest remote sensing characteristics. The field trip to Ena for a forest thinning operation with him and Professor Hiromichi Fukui was a valuable learning experience. I would like to greatly thank Dr. Satoru Sugita for his kind and instant support with server deployment and addressing other technical issues in the laboratory. I would like to express my gratitude to Dr. Tsubasa Hirakawa for the discussion and feedback regarding my research on mapping local forest attributes. I would like to extend my sincere gratitude to Dr. Shinya Yasumoto for his generous assistance in preparing various documents, including scholarship applications and housing arrangements. His kind support has been crucial for me in various aspects both before and after my arrival in Japan. I would like to thank the officers and staffs of the International Digital Earth Applied Science Research Center (IDEAS) and Chubu Institute for Advanced Study for their kind support with paperwork and technical assistance during my study. \par

I would like to thank the officers and staffs of the Division of Student Support and the Department of Engineering at Chubu University for their considerate care and immediate support throughout my student life. I wish to thank the teachers from the Center for International Affairs for providing a very helpful and necessary Japanese course for international students, aiding me in acquiring essential basic Japanese language skills for daily life. \par

My appreciation extends to my colleagues and friends at Chubu University, including Man Duc Chuc, Rie Kanai, Titipakorn Prakayapan, and Hasnat Lalon, for their generous support during my studies. I cherished the enjoyable times and discussions we shared over lunches, dinners, and trips. \par

I would like to give special thanks to Dr. Bui Quang Hung and Dr. Nguyen Thi Nhat Thanh, my former supervisors at Vietnam National University, who taught me foundational knowledge in this field and kindly introduced me to my current supervisor, Professor Hiromichi Fukui. \par

I acknowledge the funding received for my Ph.D. candidacy from the Japanese Government through the Ministry of Education, Culture, Sports, Science, and Technology (MEXT) scholarship and the funding for Ph.D. students from Chubu University. \par

For this study, all the equipment and tools I used were provided and purchased by the IDEAS center and Chubu University. \par

Finally, I express my gratitude to my family for their unconditional love and support over the years. This thesis is also their accomplishment, and I dedicate it to them. \par